Mean and variance functions used to simulate Gaussian data

### 2019-11-12 analysis/gaussian_signals.Rmd
wflow_publish("gaussian_signals.Rmd")

Define the Blip mean function.

```{r define-blip}
mu.blip = (0.32 + 0.6 * t +
           0.3 * exp(-100 * (t - 0.3)^2)) * (t >= 0 & t <= 0.8) +
  (-0.28 + 0.6 * t + 0.3 * exp(-100 * (t - 1.3)^2)) * (t > 0.8 & t <= 1)
```

Define the Corner mean function.

```{r define-corner}
mu.cor = 623.87 * t^3 * (1 - 2 * t) * (t >= 0 & t <= 0.5) +
         187.161 * (0.125 - t^3) * t^4 * (t > 0.5 & t <= 0.8) +
         3708.470441 * (t - 1)^3 * (t > 0.8 & t <= 1)
mu.cor = (0.6/(max(mu.cor) - min(mu.cor))) * mu.cor
mu.cor = mu.cor - min(mu.cor) + 0.2
```

Define the rest of the mean functions.

@@

```{r define-variance}
var1 = rep(1, n)
var2 = (1e-02 + 4 * (exp(-550 * (t - 0.2)^2) +
                     exp(-200 * (t - 0.5)^2) +
                     exp(-950 * (t - 0.8)^2)))
var3 = (1e-02 + 2 * mu.dop.var)
var4 = 1e-02 + mu.b
var5 = 1e-02 + 1 * (mu.cblk - min(mu.cblk))/max(mu.cblk)
var1 = var1/2
var2 = var2/max(var2)
var3 = var3/max(var3)
var4 = var4/max(var4)
var5 = var5/max(var5)
```

@@

```{r plot-mean-functions, fig.height=10, fig.width=6}
theme_set(theme_cowplot())
plot_grid(qplot(t,mu.sp,  geom="line",xlab="",ylab="",main="Spikes (sp)"),
          qplot(t,mu.bump,geom="line",xlab="",ylab="",main="Bumps (bump)"),
          qplot(t,mu.blk, geom="line",xlab="",ylab="",main="Blocks (blk)"),
          qplot(t,mu.ang, geom="line",xlab="",ylab="",main="Angles (ang)"),
          qplot(t,mu.dop, geom="line",xlab="",ylab="",main="Doppler (dop)"),
          qplot(t,mu.blip,geom="line",xlab="",ylab="",main="Blip (blip)"),
          qplot(t,mu.cor, geom="line",xlab="",ylab="",main="Corner (cor)"),
		  nrow = 4,ncol = 2)
```

@@

```{r plot-variance-functions, fig.height=7.5, fig.width=6}
plot_grid(
  qplot(t,var1,geom="line",xlab="",ylab="",main="Constant variance (v1)"),
  qplot(t,var2,geom="line",xlab="",ylab="",main="Triple exponential (v2)"),
  qplot(t,var3,geom="line",xlab="",ylab="",main="Doppler (v3)"),
  qplot(t,var4,geom="line",xlab="",ylab="",main="Bumps (v4)"),
  qplot(t,var5,geom="line",xlab="",ylab="",main="Clipped (v5)"),
  nrow = 3,ncol = 2)
```

>>>>

Define the "Blip" mean function.

```{r define-blip}
mu.blip = blip.fn(t,"mean")
```

Define the "Corner" mean function.

```{r define-corner}
mu.cor = cor.fn(t,"mean")
```

Define the remainder of the mean functions.

@@

```{r define-variance}
var1 = rep(1, n)
var2 = (1e-02 + 4 * (exp(-550 * (t - 0.2)^2) +
                     exp(-200 * (t - 0.5)^2) +
                     exp(-950 * (t - 0.8)^2)))
var3 = (1e-02 + 2 * mu.dop.var)
var4 = 0.01 + mu.b
var5 = 0.01 + 1 * (mu.cblk - min(mu.cblk))/max(mu.cblk)
var1 = var1/2
var2 = var2/max(var2)
var3 = var3/max(var3)
var4 = var4/max(var4)
var5 = var5/max(var5)
```

@@

```{r plot-mean-functions, fig.height=10, fig.width=6}
theme_set(theme_cowplot())
plot.signal <- function (t, y, label)
  quickplot(t,y,geom = "line",color = I("darkorange"),
            xlab = "",ylab = "",main = label)
plot_grid(plot.signal(t,mu.sp,"Spikes (sp)"),
          plot.signal(t,mu.bump,"Bumps (bump)"),
          plot.signal(t,mu.blk,"Blocks (blk)"),
          plot.signal(t,mu.ang,"Angles (ang)"),
          plot.signal(t,mu.dop,"Doppler (dop)"),
          plot.signal(t,mu.blip,"Blip (blip)"),
          plot.signal(t,mu.cor,"Corner (cor)"),
		  nrow = 4,ncol = 2)
```

@@

```{r plot-variance-functions, fig.height=7.5, fig.width=6}
plot_grid(plot.signal(t,var1,"Constant variance (v1)"),
          plot.signal(t,var2,"Triple exponential (v2)"),
          plot.signal(t,var3,"Doppler (v3)"),
		  plot.signal(t,var4,"Bumps (v4)"),
		  plot.signal(t,var5,"Clipped (v5)"),
		  nrow = 3,ncol = 2)
```
